---
title: "Ecological Monitoring Summary Data Report"
author: "**_Author names_**"
output: word_document
fontsize: 12pt
fig.width: 10
sansfont: Calibri Light

pandoc_args:
- +RTS
- -K64m
- -RTS
---

#### SUMMARY

**_Write a summary based on the results of this report_**
 
\newpage

#### INTRODUCTION

The ecological monitoring data report provides a basic analysis and interpretation of ecological data collected in coral reefs to detect changes in managed access and reserves (MA+R) across national and subnational levels. Results from ecological monitoring are critical for evaluating trends in ecosystem health and coastal fisheries, and for providing high quality data for decision-making to achieve effective and adaptive management. The ultimate objective of ecological monitoring is to assess the effectiveness of the MA+R approach in increasing fish populations and improving ecosystem health.

#### METHODOLOGY

Underwater surveys were conducted through partner universities and local organizations to characterize the marine and coastal ecosystems inside and outside of the MA+R areas. Selected fish and benthic species were recorded within representative survey areas, allowing for estimates of fish biomass and abundance, fish size structure and diversity, percent habitat cover, functional habitat diversity.

#### *Survey Locations*

We surveyed `r length(sel_maa)` managed access and reserves across **_include administrative level_**.

#### *Fish Surveys*
    
We used underwater visual census (UVC) to monitor reef fish assemblages. 

#### RESULTS

```{r fish_biomass, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if ("Fish biomass" %in% report_metrics) p$Fish[["Fish biomass"]]$plot
```

```{asis, echo="Fish biomass" %in% report_metrics}
**Figure**. Average fish biomass (± standard error) in kg/ha
```


```{r fish_density, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if ("Fish density" %in% report_metrics) p$Fish[["Fish density"]]$plot
```

```{asis echo="Fish density" %in% report_metrics}
**Figure**. Average fish density (± standard error) in individuals/ha
```


```{r fish_size, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Fish size" %in% report_metrics) p$Fish[["Fish size"]]$plot
```

```{asis echo="Fish size" %in% report_metrics}
**Figure**. Average total length (TL) of fish (± standard error) in cm
```


```{r fish_diversity, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Fish diversity" %in% report_metrics) p$Fish[["Fish diversity"]]$plot
```

```{asis echo="Fish diversity" %in% report_metrics}
**Figure**. Average number of fish species (± standard error).
```


```{r hardcoral_cover, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Coral reef cover" %in% report_metrics) p[["Coral reefs"]][["Coral reef cover"]]$plot
```

```{asis echo="Coral reef cover" %in% report_metrics}
**Figure**. Average coverage of hard corals (± standard error).
```


```{r hardcoral_diversity, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Coral reef diversity" %in% report_metrics) p[["Coral reefs"]][["Coral reef cover"]]$plot
```

```{asis echo="Coral reef diversity" %in% report_metrics}
**Figure**. Average number of benthic groups (± standard error).
```

#### CONCLUSIONS

**_Write a conclusion based on the results_**