---
title: "Ecological Monitoring Summary Data Report"
author: "**_Author names_**"
output: word_document
fontsize: 12pt
fig.width: 10
sansfont: Calibri Light

pandoc_args:
- +RTS
- -K64m
- -RTS
---

### SUMMARY

**_Write a summary based on the results of this report_**
 
\newpage

### INTRODUCTION

The ecological monitoring data report provides a basic analysis and interpretation of ecological data collected in coral reefs to detect changes in managed access and reserves (MA+R) across national and subnational levels. Results from ecological monitoring are critical for evaluating trends in ecosystem health and coastal fisheries, and for providing high quality data for decision-making to achieve effective and adaptive management. The ultimate objective of ecological monitoring is to assess the effectiveness of the MA+R approach in increasing fish populations and improving ecosystem health.

### METHODOLOGY

Underwater surveys were conducted through partner universities and local organizations to characterize the marine and coastal ecosystems inside and outside of the MA+R areas. Selected fish and benthic species were recorded within representative survey areas, allowing for estimates of fish biomass and abundance, fish size structure and diversity, percent habitat cover, functional habitat diversity.

#### *Survey Locations*

We surveyed `r length(sel_maa)` managed access and reserves across **_include administrative level_**.

#### *Fish Surveys*
    
We used underwater visual census (UVC) to monitor reef fish assemblages. 

### RESULTS

```{asis echo=any(c("Fish biomass", "Fish density", "Fish size", "Fish diversity") %in% report_metrics)}
#### Fish surveys
```

```{r fish_biomass, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if ("Fish biomass" %in% report_metrics) p$Fish[["Fish biomass"]]$plot
```

```{asis echo="Fish biomass" %in% report_metrics}
**Figure**. Average fish biomass (± standard error) in kg/ha
```


```{r fish_density, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if ("Fish density" %in% report_metrics) p$Fish[["Fish density"]]$plot
```

```{asis echo="Fish density" %in% report_metrics}
**Figure**. Average fish density (± standard error) in individuals/ha
```


```{r fish_size, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Fish size" %in% report_metrics) p$Fish[["Fish size"]]$plot
```

```{asis echo="Fish size" %in% report_metrics}
**Figure**. Average total length (TL) of fish (± standard error) in cm
```


```{r fish_diversity, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Fish diversity" %in% report_metrics) p$Fish[["Fish diversity"]]$plot
```

```{asis echo="Fish diversity" %in% report_metrics}
**Figure**. Average number of fish species (± standard error).
```


```{asis echo=any(c("Coral reef cover", "Coral reef diversity") %in% report_metrics)}
### Coral reef surveys
```

```{r coral_cover, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Coral reef cover" %in% report_metrics) p[["Coral reefs"]][["Coral reef cover"]]$plot
```

```{asis echo="Coral reef cover" %in% report_metrics}
**Figure**. Average coverage of corals and other benthic categories (± standard error).
```


```{r coral_diversity, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if("Coral reef diversity" %in% report_metrics) p[["Coral reefs"]][["Coral reef diversity"]]$plot
```

```{asis echo="Coral reef diversity" %in% report_metrics}
**Figure**. Average number of benthic groups (± standard error).
```


```{asis echo=any(c("Mangrove sapling density", "Mangrove diversity", "Mangrove size") %in% report_metrics)}
### Mangrove surveys
```

```{r mangrove_sapling, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Mangrove sapling density" %in% report_metrics) p[["Mangroves"]][["Mangrove sapling density"]]$plot
```

```{asis echo="Mangrove sapling density" %in% report_metrics}
**Figure**. Average mangrove sapling density (± standard error).
```


```{r mangrove_diversity, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Mangrove diversity" %in% report_metrics) p[["Mangroves"]][["Mangrove diversity"]]$plot
```

```{asis echo="Mangrove diversity" %in% report_metrics}
**Figure**. Average number of mangrove species (± standard error).
```


```{r mangrove_size, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Mangrove size" %in% report_metrics) p[["Mangroves"]][["Mangrove size"]]$plot
```

```{asis echo="Mangrove size" %in% report_metrics}
**Figure**. Average mangrove diameter at breast height (DBH) (± standard error).
```


```{asis echo=any(c("Seagrass cover", "Seagrass height") %in% report_metrics)}
### Seagrass surveys
```

```{r seagrass_cover, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Seagrass cover" %in% report_metrics) p[["Seagrass"]][["Seagrass cover"]]$plot
```

```{asis echo="Seagrass cover" %in% report_metrics}
**Figure**. Average seagrass cover (± standard error).
```


```{r seagrass_height, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Seagrass height" %in% report_metrics) p[["Seagrass"]][["Seagrass height"]]$plot
```

```{asis echo="Seagrass height" %in% report_metrics}
**Figure**. Average seagrass height (± standard error).
```


```{asis echo=any(c("Oyster density", "Oyster size") %in% report_metrics)}
### Oyster surveys
```

```{r oyster_density, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Oyster density" %in% report_metrics) p[["Oysters"]][["Oyster density"]]$plot
```

```{asis echo="Oyster density" %in% report_metrics}
**Figure**. Average oyster density (± standard error).
```


```{r oyster_size, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Oyster size" %in% report_metrics) p[["Oysters"]][["Oyster size"]]$plot
```

```{asis echo="Oyster size" %in% report_metrics}
**Figure**. Average oyster size (± standard error).
```

```{asis echo=any(c("Crab density", "Crab size") %in% report_metrics)}
### Crab surveys
```

```{r crab_density, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Crab density" %in% report_metrics) p[["Crabs"]][["Crab density"]]$plot
```

```{asis echo="Crab density" %in% report_metrics}
**Figure**. Average crab density (± standard error).
```


```{r crab_size, echo=FALSE, fig.height=9, fig.width=10, dpi=300, message=FALSE, warning=FALSE, pageed.print=FALSE}
if("Crab size" %in% report_metrics) p[["Crabs"]][["Crab size"]]$plot
```

```{asis echo="Crab size" %in% report_metrics}
**Figure**. Average crab carapace length (± standard error).
```

### CONCLUSIONS

**_Write a conclusion based on the results_**