---
title: "Ecological Monitoring Summary Data Report"
author: "RARE Automatic Report Generator"
output: word_document
fontsize: 12pt
fig.width: 10
sansfont: Calibri Light

pandoc_args:
- +RTS
- -K64m
- -RTS
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
report_metrics <- input$report_metrics
sel_maa <- rv$sel_maa
facet_maa <- rv$facet_maa
y_scale <- rv$sel_yscale
sel_geom <- rv$sel_geom
data_filtered <- list()
p <- list()

if (any(INIT$METRICS$Fish %in% report_metrics)) {
  sel_family <- rv$sel_family
  data_filtered[["Fish"]] <- INIT$DATA_FULL[['Fish']] %>%
    dplyr::filter(
      ma_name %in% sel_maa,
      family %in% sel_family
    )
  for (metric in INIT$METRICS$Fish) {
    if (metric %in% report_metrics) {
      p$Fish[[metric]] <- PLOT_FUN(metric, data_filtered$Fish, sel_geom, facet_maa)
      p$Fish[[metric]] <- clean_plot(p$Fish[[metric]], facet_maa, y_scale, metric, sel_maa)$p
    }
  }
}
for (survey in setdiff(names(INIT$METRICS), "Fish")) {
  if (any(INIT$METRICS[[survey]] %in% report_metrics)) {
    data_filtered[[survey]] <- INIT$DATA_FULL[[survey]] %>% 
      dplyr::filter(ma_name %in% sel_maa)
  }
}
```

\begin{aligned}
Report generated on: `r format(Sys.Date(), "%B %d, %Y")`
\end{aligned}

#### SUMMARY

{*include a summary based on the results of this report*}
 
\newpage

#### INTRODUCTION

The ecological monitoring data report provides a basic analysis and interpretation of ecological data collected in coral reefs to detect changes in managed access and reserves (MA+R) across national and subnational levels. Results from ecological monitoring are critical for evaluating trends in ecosystem health and coastal fisheries, and for providing high quality data for decision-making to achieve effective and adaptive management. The ultimate objective of ecological monitoring is to assess the effectiveness of the MA+R approach in increasing fish populations and improving ecosystem health.

#### METHODOLOGY

Underwater surveys were conducted through partner universities and local organizations to characterize the marine and coastal ecosystems inside and outside of the MA+R areas. Selected fish and benthic species were recorded within representative survey areas, allowing for estimates of fish biomass and abundance, fish size structure and diversity, percent habitat cover, functional habitat diversity.

#### *Survey Locations*

We surveyed {*include number of MA+R selected*} managed access and reserves across {*include administrative level*}.

#### *Fish Surveys*
    
We used underwater visual census (UVC) to monitor reef fish assemblages. 

#### RESULTS AND DISCUSSIONS

```{r fish_biomass, echo=FALSE, fig.height=9, fig.width=9, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if ("Fish biomass" %in% report_metrics) p$Fish[["Fish biomass"]]$plot
```
```{asis, echo="Fish biomass" %in% report_metrics}
**Figure**. Average fish biomass (± 95% confidence interval) in kg/ha
```

```{r fish_density, echo=FALSE, fig.height=9, fig.width=9, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
if ("Fish density" %in% report_metrics) p$Fish[["Fish density"]]$plot
```
```{asis echo="Fish density" %in% report_metrics}
**Figure**. Average fish density (± 95% confidence interval) in individuals/ha
```

```{r fish_size, echo=FALSE, fig.height=9, fig.width=9, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
# if("Fish Size Structure" %in% input$metrics) plotFishSize()
```

**Figure**. Size structure (total length in cm) for most common species

```{r fish_diversity, echo=FALSE, fig.height=9, fig.width=9, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
#if("Fish Diversity" %in% input$metrics) plotFishDiversity()
```

**Figure**. Averege number of fish species (± 95% confidence interval).

```{r hardcoral_cover, echo=FALSE, fig.height=9, fig.width=9, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
# if("Hard Coral Cover" %in% input$metrics)  plot_hardcoral.cover()
```

**Figure**. Averege coverage of hard corals (± 95% confidence interval).

```{r hardcoral_diversity, echo=FALSE, fig.height=9, fig.width=9, dpi=300, message=FALSE, warning=FALSE, paged.print=FALSE}
# if("Habitat Diversity" %in% input$metrics) plot_benthic.diversity()
```

**Figure**. Average number of benthic groups (± 95% confidence interval).





#### CONCLUSIONS

```{r, echo=FALSE}

```

For more information check the [Rare Data Portal](https://portal.rare.org/program-data/impacts/ecological-impacts/fisheries-recovery/ecological-data/)